### 2017-09-19 icde/sec-exp.tex

\newcommand{\graphscale}{0.36} %0.38
\newcommand{\graphmargin}{-4ex}
\newcommand{\exppath}{./exp/}
%\newcommand{\exppath}{./exp/wpr/}
%%% all in 1 Figure
\begin{figure*}[tb!]
%\vspace{-2ex}
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
%\hspace{10ex}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-futureyear}
\includegraphics[scale=\graphscale]{\exppath AAN_PairAcc1.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-t}
\includegraphics[scale=\graphscale]{\exppath AAN_PairAcc2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-fcdiff}
\includegraphics[scale=\graphscale]{\exppath AAN_PairAcc3.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-sigma}
\includegraphics[scale=\graphscale]{./exp/AAN_sigma2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-lambda}
\includegraphics[scale=\graphscale]{./exp/AAN_lambda.eps}}
\\ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-1.5ex}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-futureyear}
\includegraphics[scale=\graphscale]{\exppath AMiner_PairAcc1.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-t}
\includegraphics[scale=\graphscale]{\exppath AMiner_PairAcc2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-fcdiff}
\includegraphics[scale=\graphscale]{\exppath AMiner_PairAcc3.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-sigma}
\includegraphics[scale=\graphscale]{./exp/AMiner_sigma2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-lambda}
\includegraphics[scale=\graphscale]{./exp/AMiner_lambda.eps}}
\\%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-1.5ex}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-futureyear}
\includegraphics[scale=\graphscale]{\exppath MAG_PairAcc1.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-t}
\includegraphics[scale=\graphscale]{\exppath MAG_PairAcc2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-fcdiff}
\includegraphics[scale=\graphscale]{\exppath MAG_PairAcc3.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-sigma}
\includegraphics[scale=\graphscale]{./exp/MAG_sigma2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-lambda}
\includegraphics[scale=\graphscale]{./exp/MAG_lambda.eps}}
\end{center}
\vspace{-2.5ex}
\caption{\small Accuracy tests with \fcita (all) and \recom ((d)--(e), (i)--(j) and (n)--(o))}
\label{exp-pairacc}
\vspace{-2ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tb!]
%\vspace{1ex}
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
%\hspace{10ex}
\subfigure[{\scriptsize TWPageRank (batch vs. inc.)}]{\label{exp-aminer-time1}
\includegraphics[scale=\graphscale]{./exp/AMiner_time_twpr.eps}}
\hspace{0ex}
%\hfill
\subfigure[{\scriptsize Comparison of ranking algorithms}]{\label{exp-aminer-time2}
\includegraphics[scale=\graphscale]{./exp/AMiner_time.eps}}
\hspace{0ex}
%\hfill
\subfigure[{\scriptsize TWPageRank (batch vs. inc.)}]{\label{exp-mag-time1}
\includegraphics[scale=\graphscale]{./exp/MAG_time_twpr.eps}}
\hspace{0ex}
%\hfill
\subfigure[{\scriptsize Comparison of ranking algorithms}]{\label{exp-mag-time2}
\includegraphics[scale=\graphscale]{./exp/MAG_time.eps}}
\end{center}
\vspace{-2.5ex}
\caption{\small Efficiency tests on \aminer ((a)--(b)) and  \magdata ((c)--(d))}
\label{exp-time}
\vspace{-3ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\graphscaleexpapp}{0.25}
\newcommand{\graphmarginexpapp}{-2ex}
%%% all in 1 Figure
\begin{figure*}[tb!]
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
\subfigure[{\scriptsize \aan with \recom}]{\label{exp-aan-ab-recom}
\includegraphics[scale=\graphscaleexpapp]{./exp/AAN-para-recm.eps}}
%\quad\quad
%\hspace{\graphmarginexpapp}
\hfill
\subfigure[{\scriptsize \aminer with \recom}]{\label{exp-aminer-ab-recom}
\includegraphics[scale=\graphscaleexpapp]{./exp/AMiner-para-recm.eps}}
%\quad\quad
%\hspace{\graphmarginexpapp}
\hfill
\subfigure[{\scriptsize \magdata with \recom}]{\label{exp-mag-ab-recom}
\includegraphics[scale=\graphscaleexpapp]{./exp/MAG-para-recm.eps}}
\\ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-2ex}
%\hspace{-10ex}
\subfigure[{\scriptsize \aan  with \fcita}]{\label{exp-aan-ab-fcita}
\includegraphics[scale=\graphscaleexpapp]{./exp/AAN-para-fcita.eps}}
%\quad\quad
%\hspace{\graphmarginexpapp}
\hfill
\subfigure[{\scriptsize \aminer with \fcita}]{\label{exp-aminer-ab-fcita}
\includegraphics[scale=\graphscaleexpapp]{./exp/AMiner-para-fcita.eps}}
%\quad\quad
%\hspace{\graphmarginexpapp}
\hfill
\subfigure[{\scriptsize \magdata with \fcita}]{\label{exp-mag-ab-fcita}
\includegraphics[scale=\graphscaleexpapp]{./exp/MAG-para-fcita.eps}}
\end{center}
\vspace{-2.5ex}
\caption{\small Accuracy tests: varying aggregating parameters $\alpha$ and $\beta$}
\label{exp-ab}
\vspace{-3ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[tb!]
%\vspace{-2ex}
\begin{center}
\caption{\small Accuracy tests using different components with \recom (rows 2--4) and \fcita (rows 5--7).}
\label{tab-recom}
\begin{small}
\vspace{-.5ex}
\begin{tabular}{|c| c |c | c|}
\hline
{\bf Datasets} & {\bf C}\hspace{5ex}{\bf V}\hspace{5ex}{\bf A} & {\bf CV}\hspace{3ex}{\bf CA}\hspace{3ex}{\bf VA} & {\bf CVA} \\
\hline \hline
% \recom
\aan & 0.752 \ 0.616 \ 0.649 & 0.809 \ 0.764 \ 0.747 & {\bf 0.810} \\
\aminer & 0.735 \  0.581 \  0.640 & 0.784 \ 0.749 \ 0.729 & {\bf 0.785} \\
\magdata & 0.635 \ 0.534 \ 0.553 & 0.697 \ 0.673 \  0.648 & {\bf 0.698} \\ \hline
% \ficta
\aan & 0.785 \ 0.557 \ 0.761 & 0.849 \ 0.866 \ 0.771 & {\bf 0.870} \\
\aminer & 0.713 \  0.603 \  0.725 & 0.843 \ 0.847 \ 0.740 & {\bf 0.856} \\
\magdata & 0.736 \ 0.628 \ 0.718 & 0.848 \ 0.857 \ 0.751 & {\bf 0.874} \\
\hline
\end{tabular}
\end{small}
\end{center}
\vspace{-6ex}
\end{table}
%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tb!]
%\vspace{1ex}
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
\subfigure[{\scriptsize \aan with \recom}]{\label{exp-aan-recom-drank}
\includegraphics[scale=0.35]{./exp/AAN_TWPageRank_recom.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \aminer with \recom}]{\label{exp-aminer-recom-drank}
\includegraphics[scale=0.35]{./exp/AMiner_TWPageRank_recom.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \magdata with \recom}]{\label{exp-mag-recom-drank}
\includegraphics[scale=0.35]{./exp/MAG_TWPageRank_recom.eps}}
\\%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-1.5ex}
\subfigure[{\scriptsize \aan with \fcita}]{\label{exp-aan-fcita-drank}
\includegraphics[scale=0.35]{./exp/AAN_TWPageRank_fcita.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \aminer with \fcita}]{\label{exp-aminer-fcita-drank}
\includegraphics[scale=0.35]{./exp/AMiner_TWPageRank_fcita.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \magdata with \fcita}]{\label{exp-mag-fcita-drank}
\includegraphics[scale=0.35]{./exp/MAG_TWPageRank_fcita.eps}}
\end{center}
\vspace{-2.5ex}
\caption{\small Impacts of the TWPageRank on accuracy: varying importance weighting
factor $\lambda$}
\label{exp-drank}
\vspace{-3ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\etitle{Exp-4.4}.
\marked{To evaluate the impacts of the proposed TWPageRank, we compared our approach \ensemblerank with an algorithm alternative (referred to as \drank) the same to \ensemblerank except exploiting exponentially decayed impact weights, \ie $w(u,v)=e^{\sigma(T_u-T_v)}$ in Eq.~(\ref{eq-infl-weights}).
%The two algorithms produce the same popularity while different prestige.
To better understand the impacts, we varied the importance weighting factor $\lambda$ from 0.1 to 1. Note that the ranking results are the same when $\lambda=0$ due to the same popularity computation. The results are reported in Fig.~\ref{exp-drank}, where the numbers represent the improvement of \PairAcc by \ensemblerank over the one by \drank.}

\marked{
When varying $\lambda$, the \PairAcc of \ensemblerank is better than the one of \drank in most cases, which shows the superiority of the TWPageRank than exploiting exponentially decayed weights.
The difference of \PairAcc by the two algorithms is higher with \recom than with \fcita, since the two algorithms are using citation information to predict past and future citations with \fcita.
Moreover, algorithm \ensemblerank is consistently better than \drank when $0.5 \le \lambda \le 0.9$.
%, which, with \recom and \fcita, improves the \PairAcc by (2.88\%, 3.91\%, 3.90\%) and (0.55\%, 0.50\%, 0.22\%) on (\aan, \aminer, \magdata) on average, respectively.
The improvement decreases with the decrease of $\lambda$ as the popularity dominates the ranking with small $\lambda$, and in some cases, \drank outperforms \ensemblerank. %as the prestige and popularity orders of article pairs are more diverse for \drank than \ensemblerank.
Overall, with \recom and \fcita, \ensemblerank improves the \PairAcc over \drank by (1.78\%, 3.07\%, 3.20\%) and (0.29\%, 0.48\%, 0.11\%) on (\aan, \aminer, \magdata) on average, respectively.
}

\marked{
The TWPageRank has little impacts on efficiency, and the running time of the two algorithms only varies (6.34\%, 4.83\%) on (\aminer, \magdata) on average, respectively.}

>>>>

\newcommand{\graphscale}{0.36} %0.38
\newcommand{\graphmargin}{-4ex}
\newcommand{\exppath}{./exp/}
%\newcommand{\exppath}{./exp/wpr/}
%%% all in 1 Figure
\begin{figure*}[tb!]
%\vspace{-2ex}
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
%\hspace{10ex}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-futureyear}
\includegraphics[scale=\graphscale]{\exppath AAN_PairAcc1.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-t}
\includegraphics[scale=\graphscale]{\exppath AAN_PairAcc2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-fcdiff}
\includegraphics[scale=\graphscale]{\exppath AAN_PairAcc3.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-sigma}
\includegraphics[scale=\graphscale]{./exp/AAN_sigma2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-lambda}
\includegraphics[scale=\graphscale]{./exp/AAN_lambda.eps}}
\\ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-1.5ex}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-futureyear}
\includegraphics[scale=\graphscale]{\exppath AMiner_PairAcc1.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-t}
\includegraphics[scale=\graphscale]{\exppath AMiner_PairAcc2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-fcdiff}
\includegraphics[scale=\graphscale]{\exppath AMiner_PairAcc3.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-sigma}
\includegraphics[scale=\graphscale]{./exp/AMiner_sigma2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-lambda}
\includegraphics[scale=\graphscale]{./exp/AMiner_lambda.eps}}
\\%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-1.5ex}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-futureyear}
\includegraphics[scale=\graphscale]{\exppath MAG_PairAcc1.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-t}
\includegraphics[scale=\graphscale]{\exppath MAG_PairAcc2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-fcdiff}
\includegraphics[scale=\graphscale]{\exppath MAG_PairAcc3.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-sigma}
\includegraphics[scale=\graphscale]{./exp/MAG_sigma2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-lambda}
\includegraphics[scale=\graphscale]{./exp/MAG_lambda.eps}}
\end{center}
\vspace{-2.5ex}
\caption{\small Accuracy tests with \fcita (all) and \recom ((d)--(e), (i)--(j) and (n)--(o))}
\label{exp-pairacc}
\vspace{-2ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tb!]
%\vspace{1ex}
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
%\hspace{10ex}
\subfigure[{\scriptsize TWPageRank (batch vs. inc.)}]{\label{exp-aminer-time1}
\includegraphics[scale=\graphscale]{./exp/AMiner_time_twpr.eps}}
\hspace{0ex}
%\hfill
\subfigure[{\scriptsize Comparison of ranking algorithms}]{\label{exp-aminer-time2}
\includegraphics[scale=\graphscale]{./exp/AMiner_time.eps}}
\hspace{0ex}
%\hfill
\subfigure[{\scriptsize TWPageRank (batch vs. inc.)}]{\label{exp-mag-time1}
\includegraphics[scale=\graphscale]{./exp/MAG_time_twpr.eps}}
\hspace{0ex}
%\hfill
\subfigure[{\scriptsize Comparison of ranking algorithms}]{\label{exp-mag-time2}
\includegraphics[scale=\graphscale]{./exp/MAG_time.eps}}
\end{center}
\vspace{-2ex}
\caption{\small Efficiency tests on \aminer ((a)--(b)) and  \magdata ((c)--(d))}
\label{exp-time}
\vspace{-3ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\graphscaleexpapp}{0.25}
\newcommand{\graphmarginexpapp}{-2ex}
%%% all in 1 Figure
\begin{figure*}[tb!]
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
\subfigure[{\scriptsize \aan with \recom}]{\label{exp-aan-ab-recom}
\includegraphics[scale=\graphscaleexpapp]{./exp/AAN-para-recm.eps}}
%\quad\quad
%\hspace{\graphmarginexpapp}
\hfill
\subfigure[{\scriptsize \aminer with \recom}]{\label{exp-aminer-ab-recom}
\includegraphics[scale=\graphscaleexpapp]{./exp/AMiner-para-recm.eps}}
%\quad\quad
%\hspace{\graphmarginexpapp}
\hfill
\subfigure[{\scriptsize \magdata with \recom}]{\label{exp-mag-ab-recom}
\includegraphics[scale=\graphscaleexpapp]{./exp/MAG-para-recm.eps}}
\\ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-2ex}
%\hspace{-10ex}
\subfigure[{\scriptsize \aan  with \fcita}]{\label{exp-aan-ab-fcita}
\includegraphics[scale=\graphscaleexpapp]{./exp/AAN-para-fcita.eps}}
%\quad\quad
%\hspace{\graphmarginexpapp}
\hfill
\subfigure[{\scriptsize \aminer with \fcita}]{\label{exp-aminer-ab-fcita}
\includegraphics[scale=\graphscaleexpapp]{./exp/AMiner-para-fcita.eps}}
%\quad\quad
%\hspace{\graphmarginexpapp}
\hfill
\subfigure[{\scriptsize \magdata with \fcita}]{\label{exp-mag-ab-fcita}
\includegraphics[scale=\graphscaleexpapp]{./exp/MAG-para-fcita.eps}}
\end{center}
\vspace{-2ex}
\caption{\small Accuracy tests: varying aggregating parameters $\alpha$ and $\beta$}
\label{exp-ab}
\vspace{-3ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[tb!]
%\vspace{-2ex}
\begin{center}
\caption{\small Accuracy tests using different components with \recom (rows 2--4) and \fcita (rows 5--7).}
\label{tab-recom}
%\begin{small}
%\vspace{-.5ex}
\begin{tabular}{|c| c |c | c|}
\hline
{\bf Datasets} & {\bf C}\hspace{5ex}{\bf V}\hspace{5ex}{\bf A} & {\bf CV}\hspace{3ex}{\bf CA}\hspace{3ex}{\bf VA} & {\bf CVA} \\
\hline \hline
% \recom
\aan & 0.752 \ 0.616 \ 0.649 & 0.809 \ 0.764 \ 0.747 & {\bf 0.810} \\
\aminer & 0.735 \  0.581 \  0.640 & 0.784 \ 0.749 \ 0.729 & {\bf 0.785} \\
\magdata & 0.635 \ 0.534 \ 0.553 & 0.697 \ 0.673 \  0.648 & {\bf 0.698} \\ \hline
% \ficta
\aan & 0.785 \ 0.557 \ 0.761 & 0.849 \ 0.866 \ 0.771 & {\bf 0.870} \\
\aminer & 0.713 \  0.603 \  0.725 & 0.843 \ 0.847 \ 0.740 & {\bf 0.856} \\
\magdata & 0.736 \ 0.628 \ 0.718 & 0.848 \ 0.857 \ 0.751 & {\bf 0.874} \\
\hline
\end{tabular}
%\end{small}
\end{center}
\vspace{-4ex}
\end{table}
%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tb!]
%\vspace{1ex}
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
\subfigure[{\scriptsize \aan with \recom}]{\label{exp-aan-recom-drank}
\includegraphics[scale=0.35]{./exp/AAN_TWPageRank_recom.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \aminer with \recom}]{\label{exp-aminer-recom-drank}
\includegraphics[scale=0.35]{./exp/AMiner_TWPageRank_recom.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \magdata with \recom}]{\label{exp-mag-recom-drank}
\includegraphics[scale=0.35]{./exp/MAG_TWPageRank_recom.eps}}
\\%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-1.5ex}
\subfigure[{\scriptsize \aan with \fcita}]{\label{exp-aan-fcita-drank}
\includegraphics[scale=0.35]{./exp/AAN_TWPageRank_fcita.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \aminer with \fcita}]{\label{exp-aminer-fcita-drank}
\includegraphics[scale=0.35]{./exp/AMiner_TWPageRank_fcita.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \magdata with \fcita}]{\label{exp-mag-fcita-drank}
\includegraphics[scale=0.35]{./exp/MAG_TWPageRank_fcita.eps}}
\end{center}
\vspace{-2ex}
\caption{\small Impacts of the TWPageRank on accuracy: varying importance weighting
factor $\lambda$}
\label{exp-drank}
\vspace{-3ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\etitle{Exp-4.4}.
\marked{To evaluate the impacts of our TWPageRank, we compared our \ensemblerank with \drank, an alternative of \ensemblerank by removing the peak time in  Eq.~(\ref{eq-infl-weights}) of  TWPageRank, \ie $w(u,v)=e^{\sigma(T_u-T_v)}$. % with a directly exponentially decayed impact weights without peak times, \ie , .
%The two algorithms produce the same popularity while different prestige.
To better understand the impacts, we varied the importance weighting factor $\lambda$ from 0.1 to 1. Note that the ranking results are the same when $\lambda=0$ due to the same popularity computation. The results are reported in Fig.~\ref{exp-drank}, where the numbers represent the improvement of \PairAcc by \ensemblerank over the one by \drank.}

When varying $\lambda$, the \PairAcc of \ensemblerank is better than the one of \drank in most cases, which shows the superiority of the TWPageRank than exploiting exponentially decayed weights directly without introducing the peak time.
The \PairAcc difference of these two algorithms is higher on \recom than on \fcita, since the two algorithms are just using citation information to predict past and future citations with \fcita.
Moreover, algorithm \ensemblerank is consistently better than \drank when $0.5 \le \lambda \le 0.9$.
%, which, with \recom and \fcita, improves the \PairAcc by (2.88\%, 3.91\%, 3.90\%) and (0.55\%, 0.50\%, 0.22\%) on (\aan, \aminer, \magdata) on average, respectively.
The improvement decreases with the decrease of $\lambda$ as the popularity dominates the ranking with small $\lambda$, and in some cases, \drank outperforms \ensemblerank. %as the prestige and popularity orders of article pairs are more diverse for \drank than \ensemblerank.
Overall, with \recom and \fcita, \ensemblerank improves the \PairAcc over \drank by (1.78\%, 3.07\%, 3.20\%) and (0.29\%, 0.48\%, 0.11\%) on (\aan, \aminer, \magdata) on average, respectively.

The TWPageRank has small impacts on efficiency, and the running time of the two algorithms only varies (6.34\%, 4.83\%) on (\aminer, \magdata) on average, respectively.
